Cards persistent analysis

### 2019-12-06 cards_persistent_analysis.Rmd
Another approach

This doesn't work particularly well either for non-persistent, either selecting on eval_other or on train_and_other.

```{r}
selected_meta_true_d_3 = meta_true_d %>%
  filter(meta_task=="toggle_losers",
         !grepl("persistent", run_type)) %>%
  mutate(source_type=case_when(
    base_task_toe == "example_is_train" ~ "train",
    source == "game_straight_flush_l_0_bv_0_sr_0" ~ "eval_target",
    T ~ "eval_other")) %>%
  group_by(run_type, run, epoch, source_type) %>%
  summarize(mean_loss=mean(loss)) %>%
  ungroup() %>%
  spread(source_type, mean_loss) %>%
  mutate(train_and_other = train + eval_other) %>%
  group_by(run_type, run) %>%
  filter(train_and_other == max(train_and_other))
selected_meta_true_d_3 %>%
  arrange(desc(train_and_other))
```

>>>>

This doesn't work particularly well either for non-persistent, either selecting on eval_other or on train_and_other, but might work better with persistent
```{r}
selected_meta_true_d_2 = meta_true_d %>%
  filter(meta_task=="toggle_losers") %>%
  mutate(source_type=case_when(
    base_task_toe == "example_is_train" ~ "train",
    source == "game_straight_flush_l_0_bv_0_sr_0" ~ "eval_target",
    T ~ "eval_other")) %>%
  group_by(run_type, run, epoch, source_type) %>%
  summarize(mean_loss=mean(loss)) %>%
  ungroup() %>%
  spread(source_type, mean_loss) %>%
  mutate(train_and_other = train + eval_other) %>%
  group_by(run_type, run) %>%
  filter(train_and_other == max(train_and_other))
selected_meta_true_d_2 %>%
  arrange(desc(train_and_other))
```

Also somewhat promising:
```{r}
source_task_loss_d = loss_d %>%
  filter(task == "game_straight_flush_l_0_bv_0_sr_0:train") %>%
  select(epoch, run, run_type, loss) %>%
  rename(source_task_base_loss = loss)

selected_meta_true_d_3 = meta_true_d %>%
  filter(meta_task=="toggle_losers") %>%
  mutate(source_type=case_when(
    base_task_toe == "example_is_train" ~ "train",
    source == "game_straight_flush_l_0_bv_0_sr_0" ~ "eval_target",
    T ~ "eval_other")) %>%
  group_by(run_type, run, epoch, source_type) %>%
  summarize(mean_loss=mean(loss)) %>%
  ungroup() %>%
  spread(source_type, mean_loss) %>%
  left_join(source_task_loss_d) %>%
  mutate(source_loss_and_other = source_task_base_loss + eval_other) %>%
  group_by(run_type, run) %>%
  filter(source_loss_and_other == max(source_loss_and_other))
selected_meta_true_d_3 %>%
  arrange(desc(source_loss_and_other))
```
